An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
slightly better learner

%More formally, this approach can be defined in Algorithm~\ref{alg:plearn}. 
Note that the probability set associated with the rules, $\Pi$, contains values
ranging from 0 to 1, which are then compared against an acceptance threshold for the final output.
%\[
%\{ P\_Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ (R_1, R_2, ... , R_n) \}
%\]

>>>>

%More formally, this approach can be defined in Algorithm~\ref{alg:plearn}. 
Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm~\ref{alg:plearn} only considers
templates without mixed types; that is, the arguments of the template are all similarly typed. Adding support for
mixed types is not much more difficult.

%probability set associated with the rules, $\Pi$, contains values
%ranging from 0 to 1, which are then compared against an acceptance threshold for the final output.
%\[
%\{ P\_Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ (R_1, R_2, ... , R_n) \}
%\]
